Equalizer Programming Guide

### 2008-04-14 Developer/ProgrammingGuide/paper.tex
Programming Guide: Add custom cover page for print version
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation
Programming Guide: prepare 0.5 version
[ ] May break build
[ ] Breaks existing applications
[ ] Bugfix
[ ] New Feature
[ ] Cleanup
[ ] Optimization
[x] Documentation

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.1.12 for Equalizer 0.5-RC\\[\medskipamount]
  \today
}

@@

\thispagestyle{empty}

%\abstract{
%  Equalizer is a project to develop software to simplify the creation of
%  scalable graphics applications and to improve the usability of
%  multipipe visualization systems.
%}

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.0.1   & Nov 06, 2007 & Fixed Typo\\
    1.1     & Nov 12, 2007 & Adapted distributed objects\\
    1.1.1   & Nov 16, 2007 & Minor improvements based on lulu.com print\\
    1.1.2   & Nov 19, 2007 & Minor improvements based on feedback\\
    1.1.3   & Nov 23, 2007 & Add OpenGL extension handling\\
    1.1.4   & Nov 26, 2007 & Changes caused by removal of glX event thread\\
    1.1.5   & Dec 10, 2007 & NodeFactory API changes\\
    1.1.6   & Dec 17, 2007 & Add Scalable Rendering chapter\\
    1.1.7   & Dec 20, 2007 & Per-window object manager changes\\
    1.1.8   & Jan 15, 2008 & Detailed window initialization based on
                             latest refactoring\\
    1.1.9   & Jan 16, 2008 & Detail distributed object usage\\
    1.1.10  & Jan 28, 2008 & Add creation thread for NodeFactory entities\\
    1.1.11  & Feb 20, 2008 & Add advanced chapter for thread synchronization\\
    1.1.12  & Mar 10, 2008 & General review for 0.5 release\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

If you have any question regarding Equalizer programming, this
programming guide, or other specific problems you encountered, please
direct them to the \textsf{eq-dev} mailing list\footnote{see
  \link{http://www.equalizergraphics.com/lists.html}}.

>>>>

\date{
  \vspace{2cm}
  \begin{figure}[ht]
    \hspace{-4.5cm}\includegraphics[width=22cm]{images/teaser.pdf}
  \end{figure}
  \vspace{1cm}
%  \textbf{RELEASE CANDIDATE}\\[\medskipamount]
  Version 1.2 for Equalizer 0.5\\[\medskipamount]
  \today
}

@@

\thispagestyle{empty}
\maketitle

@@

\clearpage
\thispagestyle{empty}
\tableofcontents
\vfill{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Version for Equalizer 0.5\\
    \hline
  \end{tabularx}}
\thispagestyle{empty}
\clearpage

@@

If you have any question regarding Equalizer programming, this
programming guide, or other specific problems you encountered, please
direct them to the \textsf{eq-dev} mailing
list\footnote{\link{http://www.equalizergraphics.com/lists.html}}.
